Transcriptomic Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-05-09 Cover_letter_JPM.tex
Updates from Overleaf

***More introduction to how other researchers used TCGA to find expression biomarkers should be presented in the Introduction section. 
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
%\subsubsection{utility of TCGA}
%%%
Usually, researchers used TCGA to find expression biomarkers...
%%%%%%%%%

@@

%%%
There are three steps of biomarker discovery from survival analysis.
First, although \acrshort{tcga} genomics data was harmonized, there is unclean data, including null expressed genes, over 50\% of the cohort, should be manually investigated and cleaned.
%%% *** with more
Second, we find a way to determine candidates from the expression level of 20,500 human protein-coding genes\cite{Clamp2007}.

>>>>

***More introduction to how other researchers used TCGA to find expression biomarkers should be presented in the Introduction section. 
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
%\subsubsection{utility of TCGA}
%%%
Usually, researchers used TCGA to find expression biomarkers...
see https://www.biostars.org/p/153013/
Tutorial: Survival analysis of TCGA patients
#integrating gene expression (RNASeq) data Why would you want to do survival
#analysis based on gene expression data? Well, let's say you have a number of
#genes that you are interested in and they are differentially expressed between
#tumor and normal samples, it would be very powerful to show that alteration in
#gene expression correlates with worse survival or earlier tumor recurrence.
#https://groups.google.com/forum/m/#!msg/ucsc-cancer-genomics-browser/YvKnWZSsw1Q/3IAkkEMyFa4J
#from Mary Goldman and Jing Zhu, UCSC Cancer Browser
#https://genome-cancer.ucsc.edu/
%%%%%%%%%

@@

%%%
There are three steps of biomarker discovery from survival analysis.
First, although \acrshort{tcga} genomics data was harmonized, there is unclean data, including null expressed genes, over 50\% of the cohort, should be manually investigated and cleaned.
%%% 
{
[main_marginSFP_HNSCC.R] line 1361
=> osccT_2021 <- osccT[c(30,31)] # [30] "days_to_last_followup", [31] "days_to_last_known_alive" 
OS_live_days /30 # derived from last followup [30]/ last known alive [31])
event (alive) => censored (status 0) # to handle missing data of censored by OS_months imputation
R help from Jorge I Velez
[line 1654]
=> gene correction (20499 -> 20500) from SLC35E2A to 2 genes:
# SLC35E2A: 9906
# SLC35E2B: 728661
}

%%%
Second, we find a way to determine candidates from the expression level of 20,500 human protein-coding genes\cite{Clamp2007}.
